---
title: "Connecting Centralization to Actual Behavior"
output: html_notebook
---

# Libraries
```{r}
library(tidyverse)
library(data.table)
library(lubridate)
library(readxl)
```
# Data
```{r}
hlm_data <- fread("~/Downloads/nba_long_nets_ready_for_hlm_2.csv")
```
## Breaks Data into High Mid Low
```{r}

hlm_data <- hlm_data %>% 
  mutate(Game_Category = case_when(tot_deg_cent > .4 ~ "High",
                  tot_deg_cent < .4 & tot_deg_cent > .2 ~"Mid",
                               tot_deg_cent < .2 ~ "Low")) 


```
## High Mid Low (Entire League)
In this chunk the data is grouped in to 3 categories (High, Mid, Low). High is a game with total degree centralization greater than .4. Mid is a game with a total degree central between .2 and .4. Low is a game with a total degree centralization below .2. For each category the average of all 5 (assists, rebounds,turnovers, FG pct, FT pct) along with pass volume and plus/minus team are calculated. The descriptive for each category are as follows
```{r}

GameCategory_League_Descriptives <- function(metric, year){ 
  
   if(metric == "sd"){
         hlm_data %>% filter(yearSeason %in% year) %>% group_by(slugSeason, Game_Category) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(sd, na.rm = TRUE) 
   }
   
    else if(metric == "median"){
         hlm_data  %>% filter(yearSeason %in% year) %>% group_by(slugSeason, Game_Category) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(median, na.rm = TRUE)
    }
   
   else if(metric == "IQR"){
         hlm_data  %>% filter(yearSeason %in% year) %>% group_by(slugSeason, Game_Category) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(IQR, na.rm = TRUE) 
   }
   
   else if (metric == "mean"){
         hlm_data  %>% filter(yearSeason %in% year) %>% group_by(slugSeason, Game_Category) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(mean, na.rm = TRUE) 
   }
   
 }

GameCategory_League_Descriptives(metric = "sd", year = c(2014, 2015))

```
# Outcome of Games High Mid Low
This chunk calculates the number of wins and loses for each category of game and finds the win/loss percentage. 

High: 436 loses (.508%), 422 wins (.492%)
Mid: 4728 loses (.500%), 4739 wins (.500%)
Low: 947 loses (.494%), 969 wins (.506%)
```{r}

hlm_data %>% group_by(Game_Category, outcomeGame) %>% count() %>% group_by(Game_Category) %>% mutate(percentage = n/sum(n))

```
# Graphs High, Mid, Low (Game Category)
One interesting take away from this bar chart is that a significant amount of the games fall into the mid category (total degree central between .2 and .4).
```{r}

ggplot(data = hlm_data) + 
  geom_bar(mapping = aes(x = Game_Category))

```
## Histograms 
```{r}

hlm_data %>% filter(!is.na(Game_Category)) %>% ggplot( aes(x = astTeam, fill = Game_Category)) + 
  geom_histogram() + facet_wrap(~Game_Category, ncol = 2)

hlm_data %>% filter(!is.na(Game_Category)) %>% ggplot( aes(x = trebTeam, fill = Game_Category)) + 
  geom_histogram() + facet_wrap(~Game_Category, ncol = 2)

hlm_data %>% filter(!is.na(Game_Category)) %>% ggplot( aes(x = tovTeam, fill = Game_Category)) + 
  geom_histogram() + facet_wrap(~Game_Category, ncol = 2)

hlm_data %>% filter(!is.na(Game_Category)) %>% ggplot( aes(x = pctFGTeam, fill = Game_Category)) + 
  geom_histogram() + facet_wrap(~Game_Category, ncol = 2)

hlm_data %>% filter(!is.na(Game_Category)) %>% ggplot( aes(x = pctFTTeam, fill = Game_Category)) + 
  geom_histogram() + facet_wrap(~Game_Category, ncol = 2)

hlm_data %>% filter(!is.na(Game_Category)) %>% ggplot( aes(x = pass_vol, fill = Game_Category)) + 
  geom_histogram() + facet_wrap(~Game_Category, ncol = 2)

hlm_data %>% filter(!is.na(Game_Category)) %>% ggplot( aes(x = plusminusTeam, fill = Game_Category)) + 
  geom_histogram() + facet_wrap(~Game_Category, ncol = 2)

```
## Indvidual Teams Function 
```{r}

```
# Indiviual Teams Five Factors Variability (<.2) (Low)

This chunk groups the data by each team and calculates the mean, median, standard deviation, and IQR of the all 7 variables 
```{r}

GameCategory_Low_Descriptives <- function(metric, year){ 
  
   if(metric == "sd"){
         hlm_data %>% filter(yearSeason %in% year) %>% filter(tot_deg_cent < .2) %>% group_by(TEAM_NAME, slugSeason) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(sd, na.rm = TRUE) 
   }
   
    else if(metric == "median"){
         hlm_data  %>% filter(yearSeason %in% year) %>% filter(tot_deg_cent < .2) %>% group_by(TEAM_NAME, slugSeason) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(median, na.rm = TRUE)
    }
   
   else if(metric == "IQR"){
         hlm_data  %>% filter(yearSeason %in% year) %>% filter(tot_deg_cent < .2) %>% group_by(TEAM_NAME, slugSeason) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(IQR, na.rm = TRUE) 
   }
   
   else if (metric == "mean"){
         hlm_data  %>% filter(yearSeason %in% year) %>% filter(tot_deg_cent < .2) %>% group_by(TEAM_NAME, slugSeason) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(mean, na.rm = TRUE) 
   }
   
 }

GameCategory_Low_Descriptives(metric = "mean", year = c(2014, 2015))

```
## Histograms
```{r}

hlm_data %>% filter(tot_deg_cent < .2) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x = astTeam)) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

hlm_data %>% filter(tot_deg_cent < .2) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x = trebTeam)) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

hlm_data %>% filter(tot_deg_cent < .2) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x = tovTeam)) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

hlm_data %>% filter(tot_deg_cent < .2) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x = pctFGTeam)) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

hlm_data %>% filter(tot_deg_cent < .2) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x =pctFTTeam )) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

hlm_data %>% filter(tot_deg_cent < .2) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x = pass_vol)) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

hlm_data %>% filter(tot_deg_cent < .2) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x = plusminusTeam)) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

```
# Indiviual Teams Five Factors Variability (<.4 and >.2) (Mid)
```{r}

GameCategory_Mid_Descriptives <- function(metric, year){ 
  
   if(metric == "sd"){
         hlm_data %>% filter(yearSeason %in% year) %>% filter(tot_deg_cent < .4 & tot_deg_cent > .2) %>% group_by(TEAM_NAME, slugSeason) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(sd, na.rm = TRUE) 
   }
   
    else if(metric == "median"){
         hlm_data  %>% filter(yearSeason %in% year) %>% filter(tot_deg_cent < .4 & tot_deg_cent > .2) %>% group_by(TEAM_NAME, slugSeason) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(median, na.rm = TRUE)
    }
   
   else if(metric == "IQR"){
         hlm_data  %>% filter(yearSeason %in% year) %>% filter(tot_deg_cent < .4 & tot_deg_cent > .2) %>% group_by(TEAM_NAME, slugSeason) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(IQR, na.rm = TRUE) 
   }
   
   else if (metric == "mean"){
         hlm_data  %>% filter(yearSeason %in% year) %>% filter(tot_deg_cent < .4 & tot_deg_cent > .2) %>% group_by(TEAM_NAME, slugSeason) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(mean, na.rm = TRUE) 
   }
   
 }

GameCategory_Mid_Descriptives(metric = "mean", year = c(2014, 2015))

```
## Histograms 
```{r}

hlm_data %>% filter(tot_deg_cent < .4 & tot_deg_cent > .2) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x = astTeam)) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

hlm_data %>% filter(tot_deg_cent < .4 & tot_deg_cent > .2) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x = trebTeam)) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

hlm_data %>% filter(tot_deg_cent < .4 & tot_deg_cent > .2) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x = tovTeam)) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

hlm_data %>% filter(tot_deg_cent < .4 & tot_deg_cent > .2) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x = pctFGTeam)) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

hlm_data %>% filter(tot_deg_cent < .4 & tot_deg_cent > .2) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x =pctFTTeam )) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

hlm_data %>% filter(tot_deg_cent < .4 & tot_deg_cent > .2) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x = pass_vol)) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

hlm_data %>% filter(tot_deg_cent < .4 & tot_deg_cent > .2) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x = plusminusTeam)) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

```
# Individual Teams Five Factors Variability (>.4) (High)
```{r}

GameCategory_High_Descriptives <- function(metric, year){ 
  
   if(metric == "sd"){
         hlm_data %>% filter(yearSeason %in% year) %>% filter(tot_deg_cent > .4) %>% group_by(TEAM_NAME, slugSeason) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(sd, na.rm = TRUE) 
   }
   
    else if(metric == "median"){
         hlm_data  %>% filter(yearSeason %in% year) %>% filter(tot_deg_cent > .4) %>% group_by(TEAM_NAME, slugSeason) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(median, na.rm = TRUE)
    }
   
   else if(metric == "IQR"){
         hlm_data  %>% filter(yearSeason %in% year) %>% filter(tot_deg_cent > .4) %>% group_by(TEAM_NAME, slugSeason) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(IQR, na.rm = TRUE) 
   }
   
   else if (metric == "mean"){
         hlm_data  %>% filter(yearSeason %in% year) %>% filter(tot_deg_cent > .4) %>% group_by(TEAM_NAME, slugSeason) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(mean, na.rm = TRUE) 
   }
   
 }

GameCategory_High_Descriptives(metric = "mean", year = c(2014, 2015))

```
## Histograms
```{r}

hlm_data %>% filter(tot_deg_cent > .4) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x = astTeam)) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

hlm_data %>% filter(tot_deg_cent > .4) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x = trebTeam)) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

hlm_data %>% filter(tot_deg_cent > .4) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x = tovTeam)) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

hlm_data %>% filter(tot_deg_cent > .4) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x = pctFGTeam)) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

hlm_data %>% filter(tot_deg_cent > .4) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x =pctFTTeam )) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

hlm_data %>% filter(tot_deg_cent > .4) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x = pass_vol)) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

hlm_data %>% filter(tot_deg_cent > .4) %>% group_by(TEAM_ABBREVIATION) %>% ggplot(aes(x = plusminusTeam)) +
  geom_histogram() + facet_wrap(~TEAM_ABBREVIATION)

```
3) Describe (minimum, maximum, median, mean, 25th percentile and 75th percentile) of the degree centralization for all of the data
 
Maximum: .621
Minimum: 0
Median: .274
Mean: .279
25th percentile: .222
75th percentile: .330
```{r}

hlm_data %>% select(tot_deg_cent) %>% summarise(
    Minimum = min(tot_deg_cent, na.rm = TRUE), 
    Maximum = max(tot_deg_cent, na.rm = TRUE), 
    Mean = mean(tot_deg_cent, na.rm = TRUE), 
    Median = median(tot_deg_cent, na.rm = TRUE))

hlm_data %>% select(tot_deg_cent) %>% summarise(Sum = fivenum(tot_deg_cent, na.rm = TRUE))

```
#Games that don't have centralization
```{r}
hlm_data %>% filter(tot_deg_cent < .01)
```
## Turnover gap in graphs)
```{r}

hlm_data %>% group_by(Game_Category) %>% select(tovTeam)

hlm_data %>% filter(!is.na(Game_Category)) %>% ggplot( aes(x = tovTeam, fill = Game_Category)) + 
  geom_density() + facet_wrap(~Game_Category, ncol = 2)

hlm_data %>% filter(tovTeam == 15) 
                                                                        
hlm_data %>% filter(!is.na(Game_Category)) %>% count(Game_Category, tovTeam) 

print(hlm_data)

```
## Testing Area 
```{r}

GameCategory_Team_Descriptives <- function(metric, team){ 
  
   if(metric == "sd"){
         hlm_data %>% group_by(TEAM_ABBREVIATION, Game_Category) %>% filter(TEAM_ABBREVIATION == team) %>% group_by(Game_Category) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(sd, na.rm = TRUE) 
   }
   
    else if(metric == "median"){
         hlm_data %>% group_by(TEAM_ABBREVIATION, Game_Category) %>% filter(TEAM_ABBREVIATION == team) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(median, na.rm = TRUE)
    }
   
   else if(metric == "IQR"){
         hlm_data %>% group_by(TEAM_ABBREVIATION, Game_Category) %>% filter(TEAM_ABBREVIATION == team) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(IQR, na.rm = TRUE) 
   }
   
   else if (metric == "mean"){
         hlm_data %>% group_by(TEAM_ABBREVIATION, Game_Category) %>% filter(TEAM_ABBREVIATION == team) %>% select(astTeam, trebTeam, tovTeam, pctFGTeam, pctFTTeam, tot_deg_cent, pass_vol, plusminusTeam) %>% summarise_all(mean, na.rm = TRUE) 
   }
   
 }

Team_Descriptives(metric = "sd", team = "ATL")

```

