---
title: "NBA time-series 16-30"
output: html_notebook
---


```{r}
library(tidyverse)
library(data.table)
library(fpp3)
lag_data <- read_rds("/Users/diede/OneDrive/Documents/GitHub/NBA-Centralization/team_w_lags.rds")
```


```{r}
team_lag_graphs <- function(team_abrev){
  lag_data %>% ungroup() %>%
  filter(TEAM_ABBREVIATION == team_abrev, !is.na(tot_deg_cent)) %>%
  arrange(slugSeason, numberGameTeamSeason) %>%
  as_tsibble(key = c(slugSeason, TEAM_ABBREVIATION), index = c(numberGameTeamSeason)) %>%
  fill_gaps(.full = TRUE) %>%
  ACF(tot_deg_cent) %>%
  autoplot()
}
```



```{r}
relevant_team_lags <- function(team_abrev){
  important_ACF_values <- data.frame()
  team_temp_chart <- lag_data %>% ungroup() %>%
    filter(TEAM_ABBREVIATION == team_abrev, !is.na(tot_deg_cent)) %>%
    arrange(slugSeason, numberGameTeamSeason) %>%
    as_tsibble(key = c(slugSeason, TEAM_ABBREVIATION), index = c(numberGameTeamSeason)) %>%
    fill_gaps(.full = TRUE) %>%
    ACF(tot_deg_cent) 
      
  counter = 1
  for (i in 1:nrow(team_temp_chart[,4])) {
    if(team_temp_chart[[i,4]] > .2 | team_temp_chart[[i,4]] < (-.2)) {
      for (k in 1:ncol(team_temp_chart[1,])) {
        important_ACF_values[counter,k] <- team_temp_chart[i,k]
      }
      counter = counter + 1
    }
  }
  return(important_ACF_values)
}
```

```{r}
relevant_team_lags("WAS")
```


#Top and botton team lag analysis 13-14 season
```{r}
#top teams
relevant_team_lags("SAS")
relevant_team_lags("OKC")
relevant_team_lags("LAC")
relevant_team_lags("IND")
relevant_team_lags("HOU")
relevant_team_lags("MIA")
relevant_team_lags("POR")
relevant_team_lags("GSW")
relevant_team_lags("MEM")
relevant_team_lags("DAL")

#Middle 10 teams
relevant_team_lags("CHI")
relevant_team_lags("TOR")
relevant_team_lags("PHX")
relevant_team_lags("BKN")
relevant_team_lags("WAS")
relevant_team_lags("CHA")
relevant_team_lags("MIN")
relevant_team_lags("ATL")
relevant_team_lags("NYK")
relevant_team_lags("DEN")

#Bottom teams
relevant_team_lags("NOP")
relevant_team_lags("CLE")
relevant_team_lags("DET")
relevant_team_lags("SAC")
relevant_team_lags("LAL")
relevant_team_lags("BOS")
relevant_team_lags("UTA")
relevant_team_lags("ORL")
relevant_team_lags("PHI")
relevant_team_lags("MIL")
```
#Top and botton team lag analysis 13-14 season    Bovada
Place  |    Team    |   Lags             |       P(W) vs A(W) (O/U W)
  1         SAS         5                         P(55.5) A(62) (+6.5)    t5
  2         OKC         -                         P(52.5) A(59) (+6.5)    t5
  3         LAC         1                         P(56.5) A(57) (+.5)
  4         IND         -                         P(54.5) A(56) (+1.5)
  5         HOU         -                         P(54.5) A(54) (-.5)
  6         MIA         1,6,7,9,10,14,16          P(61.5) A(54) (-7.5)
  7         POR         -                         P(38.5) A(54) (+15.5)   3
  8         GSW         5                         P(51.5) A(51) (-.5)
  9         MEM         2,10                      P(50.5) A(50) (-.5)
  10        DAL         4                         P(43.5) A(49) (+5.5)
Place  |    Team    |   Lags             |       P(W) vs A(W) (O/U W)
  11        CHI         -                         P(56.5) A(48) (-8.5)
  12        TOR         7,11,13                   P(36.5) A(48) (+11.5)   4
  13        PHX         -                         P(19.5) A(48) (+28.5)   1
  14        BKN         4                         P(52.5) A(44) (-7.5)
  15        WAS         -                         P(40.5) A(44) (+3.5)
  16        CHA         1                         P(26.5) A(43) (+16.5)   2
  17        MIN         -                         P(41.5) A(40) (-1.5)
  18        ATL         17                        P(39.5) A(38) (-1.5)
  19        NYK         11                        P(48.5) A(37) (-11.5)   t28
  20        DEN         1,2,4                     P(45.5) A(36) (-9.5)    t26
Place  |    Team    |   Lags             |       P(W) vs A(W) (O/U W)
  21        NOP         16                        P(39.5) A(34) (-5.5)
  22        CLE         4,8                       P(40.5) A(33) (-7.5)
  23        DET         -                         P(40.5) A(29) (-11.5)   t28
  24        SAC         N/A                       P(31.5) A(28) (-3.5)
  25        LAL         2                         P(36.5) A(27) (-9.5)    t26
  26        BOS         -                         P(27.5) A(25) (-2.5)
  27        UTA         12                        P(25.5) A(25) (-.5)
  28        ORL         1                         P(23.5) A(23) (-.5)
  29        PHI         12                        P(16.5) A(19) (+2.5)
  30        MIL         2,12                      P(28.5) A(15) (-13.5)   30
  
-San Antonio Won title
-4/10 teams were unpredictable of the teams with the 10 best records
-6/10 teams were unpredictable of the teams with the middle 10 records
-6/9 teams were unpredictable of rhe teams with the 9 worst records

-top 5 over acheiving teams: 
  PHX +28.5
  CHA +16.5
  POR +15.5
  TOR +11.5
  SAS +6.5
  OKC +6.5
######################################################################


#Top and botton team lag analysis 14-15 season
```{r}
#top teams
relevant_team_lags("GSW")
relevant_team_lags("ATL")
relevant_team_lags("HOU")
relevant_team_lags("LAC")
relevant_team_lags("MEM")
relevant_team_lags("SAS")
relevant_team_lags("CLE")
relevant_team_lags("POR")
relevant_team_lags("CHI")
relevant_team_lags("DAL")

#Middle 10 teams
relevant_team_lags("TOR")
relevant_team_lags("WAS")
relevant_team_lags("NOP")
relevant_team_lags("OKC")
relevant_team_lags("MIL")
relevant_team_lags("BOS")
relevant_team_lags("PHX")
relevant_team_lags("BKN")
relevant_team_lags("IND")
relevant_team_lags("UTA")

#Bottom teams
relevant_team_lags("MIA")
relevant_team_lags("CHA")
relevant_team_lags("DET")
relevant_team_lags("DEN")
relevant_team_lags("SAC")
relevant_team_lags("ORL")
relevant_team_lags("LAL")
relevant_team_lags("PHI")
relevant_team_lags("NYK")
relevant_team_lags("MIN")
```
#Top and botton team lag analysis 14-15 season    Bovada
Place  |    Team    |   Lags             |       P(W) vs A(W) (O/U W)
  1         GSW         -                         P(50.5) A(67) (+16.5)   3
  2         ATL         4,17                      P(41.0) A(60) (+19.0)   1
  3         HOU         16                        P(49.5) A(56) (+6.5)
  4         LAC         -                         P(54.5) A(56) (+1.5)
  5         MEM         -                         P(49.0) A(55) (+6.0)
  6         SAS         2                         P(57.0) A(55) (-2.0)
  7         CLE         -                         P(58.5) A(53) (-5.5)
  8         POR         3,10                      P(49.0) A(51) (+2.0)
  9         CHi         -                         P(54.5) A(50) (-4.5)
  10        DAL         6,7,19                    P(49.5) A(50) (+0.5)
Place  |    Team    |   Lags             |       P(W) vs A(W) (O/U W)
  11        TOR         -                         P(48.5) A(49) (+0.5)
  12        WAS         -                         P(50.0) A(46) (-4.0)
  13        NOP         6                         P(43.0) A(45) (+2.0)
  14        OKC         2,4,6                     P(57.5) A(45) (-12.5)
  15        MIL         1,2,13                    P(24.0) A(41) (+17.0)   2
  16        BOS         11                        P(26.5) A(40) (+13.5)   5
  17        PHX         1,3,13                    P(44.0) A(39) (-5.0)
  18        BKN         13                        P(41.5) A(38) (-3.5)
  19        IND         1,2                       P(33.0) A(38) (+5.0)
  20        UTA         -                         P(24.0) A(38) (+14.0)   4
Place  |    Team    |   Lags             |       P(W) vs A(W) (O/U W)
  21        MIA         13,16                     P(44.0) A(37) (-7.0)
  22        CHA         -                         P(45.0) A(33) (-12.0)   29
  23        DET         4                         P(35.5) A(32) (-3.5)
  24        DEN         12                        P(41.5) A(30) (-11.5)   t27
  25        SAC         N/A                       P(29.5) A(29) (-0.5)
  26        ORL         5,12                      P(27.5) A(25) (-2.5)
  27        LAL         -                         P(32.5) A(21) (-11.5)   t27
  28        PHI         1,7                       P(15.5) A(18) (+2.5)
  29        NYK         -                         P(40.5) A(17) (-23.5)   30
  30        MIN         1,2,3,4,5,7,14,16         P(26.5) A(16) (-10.5)   26

-Golden State won the title
-6/10 teams were unpredictable of the teams with the best 10 records
-5/10 teams were unpredictable of the teams with the middle 10 records
-5/9 teams were unpredictable of the teams with the worst 9 records

################################################################

#Top and botton team lag analysis 15-16 season
```{r}
#top teams
relevant_team_lags("GSW")
relevant_team_lags("SAS")
relevant_team_lags("CLE")
relevant_team_lags("TOR")
relevant_team_lags("OKC")
relevant_team_lags("LAC")
relevant_team_lags("ATL")
relevant_team_lags("BOS")
relevant_team_lags("CHA")
relevant_team_lags("MIA")

#Middle 10 teams
relevant_team_lags("IND")
relevant_team_lags("DET")
relevant_team_lags("POR")
relevant_team_lags("DAL")
relevant_team_lags("MEM")
relevant_team_lags("CHI")
relevant_team_lags("HOU")
relevant_team_lags("WAS")
relevant_team_lags("UTA")
relevant_team_lags("ORL")

#Bottom teams
relevant_team_lags("DEN")
relevant_team_lags("MIL")
relevant_team_lags("SAC")
relevant_team_lags("NYK")
relevant_team_lags("NOP")
relevant_team_lags("MIN")
relevant_team_lags("PHX")
relevant_team_lags("BKN")
relevant_team_lags("LAL")
relevant_team_lags("PHI")
```
#Top and botton team lag analysis 15-16 season    Westgate
Place  |    Team    |   Lags             |       P(W) vs A(W) (O/U W)
  1         GSW         7                         P(60.5) A(73) (+12.5)   3
  2         SAS         1,2                       P(58.5) A(67) (+8.5)
  3         CLE         -                         P(56.5) A(57) (+0.5)
  4         TOR         -                         P(45.5) A(56) (+10.5)   t4
  5         OKC         4,11                      P(57.5) A(55) (-2.5)
  6         LAC         -                         P(56.5) A(53) (-3.5)
  7         ATL         13                        P(49.5) A(48) (-1.5)
  8         BOS         2                         P(42.5) A(48) (+5.5)
  9         CHA         -                         P(32.5) A(48) (+15.5)   2
  10        MIA         -                         P(45.5) A(48) (+2.5)
Place  |    Team    |   Lags             |       P(W) vs A(W) (O/U W)
  11        IND         1,8,15                    P(42.5) A(45) (+2.5)
  12        DET         4,6,7,10,11               P(33.5) A(44) (+10.5)   t4
  13        POR         -                         P(26.5) A(44) (+17.5)   1
  14        DAL         1                         P(38.5) A(42) (+3.5)
  15        MEM         -                         P(50.5) A(42) (-8.5)
  16        CHI         11                        P(49.5) A(42) (-7.5)
  17        HOU         1,2,3,4,5,6,7,8,9         P(54.5) A(41) (-13.5)   29
  18        WAS         9                         P(45.5) A(41) (-4.5)
  19        UTA         17                        P(40.5) A(40) (-0.5)
  20        ORL         -                         P(32.5) A(35) (+2.5)
Place  |    Team    |   Lags             |       P(W) vs A(W) (O/U W)
  21        DEN         4,10                      P(26.5) A(33) (+6.5)
  22        MIL         9                         P(43.5) A(33) (-10.5)
  23        SAC         N/A                       P(30.5) A(33) (+2.5)
  24        NYK         1,2,3,5                   P(31.5) A(32) (+0.5)
  25        NOP         1,11                      P(47.5) A(30) (-17.5)   30
  26        MIN         -                         P(25.5) A(29) (+3.5)
  27        PHX         5,14                      P(36.5) A(23) (-13.5)   28
  28        BKN         13                        P(28.5) A(21) (-7.5)
  29        LAL         1,2                       P(29.5) A(17) (-12.5)   27
  30        PHI         10                        P(21.5) A(10) (-11.5)   26

-Cleveland won title
-6/10 teams were unpredictable of the teams with the 10 best records
-6/10 teams were unpredictable of the teams with the middle 10 records
-4/9 teams were unpredictable of the teams with the 9 best records

##################################################################


#Top and botton team lag analysis 16-17 season
```{r}
#top teams
relevant_team_lags("GSW")
relevant_team_lags("SAS")
relevant_team_lags("HOU")
relevant_team_lags("BOS")
relevant_team_lags("CLE")
relevant_team_lags("LAC")
relevant_team_lags("TOR")
relevant_team_lags("UTA")
relevant_team_lags("WAS")
relevant_team_lags("OKC")

#Middle 10 teams
relevant_team_lags("ATL")
relevant_team_lags("MEM")
relevant_team_lags("IND")
relevant_team_lags("MIL")
relevant_team_lags("CHI")
relevant_team_lags("POR")
relevant_team_lags("MIA")
relevant_team_lags("DEN")
relevant_team_lags("DET")
relevant_team_lags("CHA")

#Bottom teams
relevant_team_lags("NOP")
relevant_team_lags("DAL")
relevant_team_lags("SAC")
relevant_team_lags("MIN")
relevant_team_lags("NYK")
relevant_team_lags("ORL")
relevant_team_lags("PHI")
relevant_team_lags("LAL")
relevant_team_lags("PHX")
relevant_team_lags("BKN")
```
#Top and botton team lag analysis 16-17 season    Bovada                O/U rank
Place  |    Team    |   Lags             |       P(W) vs A(W) (O/U W)
  1         GSW         12                        P(66.5) A(67) (+0.5)
  2         SAS         -                         P(58.5) A(61) (+2.5)
  3         HOU         2,9                       P(44.0) A(55) (+11.0)   1
  4         BOS         6,8,14                    P(52.5) A(53) (+0.5)
  5         CLE         2                         P(56.5) A(51) (-5.5)
  6         LAC         4                         P(53.5) A(51) (-2.5)
  7         TOR         3,6                       P(50.5) A(51) (+0.5)
  8         UTA         -                         P(49.0) A(51) (+2.0)
  9         WAS         -                         P(42.5) A(49) (+6.5)    t3
  10        OKC         2,17                      P(43.5) A(47) (+3.5)    t5
Place  |    Team    |   Lags             |       P(W) vs A(W) (O/U W)
  11        ATL         1,5,6                     P(43.5) A(43) (-0.5)
  12        MEM         -                         P(42.5) A(43) (+0.5)
  13        IND         2,17,18                   P(44.5) A(42) (-2.5)
  14        MIL         1,4                       P(34.5) A(42) (+7.5)    2
  15        CHI         2                         P(38.5) A(41) (+2.5)
  16        POR         12                        P(45.5) A(41) (-4.5)
  17        MIA         -                         P(34.5) A(41) (+6.5)    t3
  18        DEN         9,15                      P(37.0) A(40) (+3.0)
  19        DET         3,5                       P(44.5) A(37) (-7.5)    t27
  20        CHA         -                         P(42.5) A(36) (-6.5)    26
Place  |    Team    |   Lags             |       P(W) vs A(W) (O/U W)
  21        NOP         -                         P(37.0) A(34) (-3.0)
  22        DAL         10,11,18                  P(38.5) A(33) (-5.5)
  23        SAC         N/A                       P(34.0) A(32) (-2.0)
  24        MIN         -                         P(40.5) A(31) (-9.5)    30
  25        NYK         3                         P(38.5) A(31) (-7.5)    t27
  26        ORL         -                         P(37.5) A(29) (-8.5)    29
  27        PHI         -                         P(24.5) A(28) (+3.5)    t5
  28        LAL         -                         P(24.5) A(26) (+1.5)
  29        PHX         -                         P(30.0) A(24) (-6.0)
  30        BKN         -                         P(20.5) A(20) (-0.5)

-Golden state won title
-4/10 teams were unpredictable of the teams with the 10 best records
-5/10 teams were unpredictable of the teams with the middle 10 records
-8/9 teams were unpredictable of the teams with the 9 worst records

####################################################################



#Top and botton team lag analysis 17-18 season
```{r}
#top teams
relevant_team_lags("HOU")
relevant_team_lags("TOR")
relevant_team_lags("GSW")
relevant_team_lags("BOS")
relevant_team_lags("PHI")
relevant_team_lags("CLE")
relevant_team_lags("POR")
relevant_team_lags("IND")
relevant_team_lags("NOP")
relevant_team_lags("OKC")

#Middle 10 teams
relevant_team_lags("UTA")
relevant_team_lags("MIN")
relevant_team_lags("SAS")
relevant_team_lags("DEN")
relevant_team_lags("MIA")
relevant_team_lags("MIL")
relevant_team_lags("WAS")
relevant_team_lags("LAC")
relevant_team_lags("DET")
relevant_team_lags("CHA")

#Bottom teams
relevant_team_lags("LAL")
relevant_team_lags("NYK")
relevant_team_lags("BKN")
relevant_team_lags("CHI")
relevant_team_lags("SAC")
relevant_team_lags("ORL")
relevant_team_lags("ATL")
relevant_team_lags("DAL")
relevant_team_lags("MEM")
relevant_team_lags("PHX")
```
#Top and botton team lag analysis 17-18 season    Bovada
Place  |    Team    |   Lags             |       P(W) vs A(W) (O/U W)
  1         HOU         3,18                      P(55.5) A(65) (+9.5)    4
  2         TOR         13                        P(48.5) A(59) (+10.5)   t2
  3         GSW         -                         P(67.5) A(58) (-9.5)    28
  4         BOS         -                         P(55.5) A(55) (-0.5)
  5         PHI         -                         P(41.5) A(52) (+10.5)   t2
  6         CLE         14                        P(53.5) A(50) (-3.5)
  7         POR         3,10,13,19                P(42.5) A(49) (+6.5)
  8         IND         17                        P(31.5) A(48) (+16.5)   1
  9         NOP         17                        P(39.5) A(48) (+8.5)
  10        OKC         -                         P(50.5) A(48) (-2.5)
Place  |    Team    |   Lags             |       P(W) vs A(W) (O/U W)
  11        UTA         16                        P(41.0) A(48) (+9.0)    5
  12        MIN         -                         P(48.5) A(47) (-1.5)
  13        SAS         12,15,16                  P(54.5) A(47) (-7.5)
  14        DEN         -                         P(45.5) A(46) (+0.5)
  15        MIA         -                         P(43.5) A(44) (+0.5)
  16        MIL         12                        P(47.5) A(44) (-3.5)
  17        WAS         4,10,11,14,19             P(48.0) A(43) (-5.0)
  18        LAC         1                         P(43.5) A(42) (-1.5)
  19        DET         -                         P(38.5) A(39) (+0.5)
  20        CHA         17                        P(42.5) A(36) (-6.5)
Place  |    Team    |   Lags             |       P(W) vs A(W) (O/U W)
  21        LAL         -                         P(33.5) A(35) (+1.5)
  22        NYK         -                         P(30.5) A(29) (-1.5)
  23        BKN         1,4,6                     P(27.5) A(28) (+0.5)
  24        CHI         -                         P(22.5) A(27) (+4.5)
  25        SAC         N/A                       P(27.5) A(27) (-0.5)
  26        ORL         -                         P(33.5) A(25) (-8.5)    27
  27        ATL         17                        P(25.5) A(24) (-1.5)
  28        DAL         13                        P(35.5) A(24) (-11.5)   29
  29        MEM         1,7,11                    P(37.5) A(22) (-15.5)   30
  30        PHX         2                         P(29.0) A(21) (-8.0)    26

-Golden State won title
-8/10 teams were unpredictable of the teams with the 10 best records
-8/10 teams were unpredictable of the teams with the 10 best records
-6/9 teams were unpredictable of the teams with the 9 worst records
-7/15 of the top three teams were unpredictable

#################################################################
#OVerall analysis
-over 5 seasons teams with the 10 best records were 28/50 or 56% of them were unpredictable
-over 5 seasons teams with the middle 10 recrods were 30/50 or 60% of them were unpredictable
-over 5 season teams with the 9 worst records were 29/45 or 64.4% of the time were unpredictable

```{r}
team_lag_graphs("MIA")
relevant_team_lags("MIA")
```


#Miami
The 13-14 season the one game lag is of significance. It is positive meaning they had similar centralization on a game to game basis. The 6 and 7 lag has a significant level but is negative indicating a change in the centralization. 9 and 10 game lag is also significant with the centralization changing on 9 and 10 game lag. 14 and 16 game lag is significant on same centralizaion. The Heats record this year was 54-28 and was the final season that the big three were all together.
The 14-15 season had significant positive lag for 13 and 17 games. Their record this year was 37-45
The remainder of the data didn't have any significant lags. The Heats records for those years were 48-34, 41-41, and 44-38 for the last three seasons of the data set respectively




```{r}
team_lag_graphs("MIL")
```

#Milwaukee
13-14 season has a signigicant positive lag for 2 games. The only other significant lag was for 12 game lag in the negative. Their record this year was 15-67
14-15 season had high significence in the 1 and 2 game lags for the positive. These two were very strong as they are well above the .2 threshhold. 13 game lag is signigficant in the negative. They went 41-41.
15-16 season they only had one significant lag which was 9 games. It was in the positive. Their record was 33-49
16-17 season there were two significant lags for 1 and 4 games. Both of these were in the negative so centralization changed. They went 42 and 40 this year.
17-18 season saw no significant lag trends. they went 44-38


```{r}
team_lag_graphs("MIN")
```

#Minnesota
13-14 season there were no significant lag trends and they went 40-42
14-15 season they had a very unique. They 7-8 significant lags all of which are in the positive. Not a signle line is in the negative. They did not change anything across any period of time. Lag for 1-4 and maybe 5 are all positive. THey had a record of 16-66
15-16 season there are no significant change and had a record of 29-53.
16-17 season there are no significant change and had record of 31-51. Have had a different coach each of the four years.
17-18 season the 2 game lag might be significant in the negative. This is the first sesaon they have the same coach from the previous season. Went 47-35


```{r}
team_lag_graphs("NOP")
```

#New Oreleans
13-14 there was a significant centralization change for the 16 game lag but that is the only one. They went 34-48 that year.
14-15 season there was a significant change in centralization for 6 game lag but again that is the only one. They went 45-37. 
15-16 season there was common centralization for 1 game lag as well as 11 game lag. they went 30-52
16-17 season there was no significant point. they went 34-48.
17-18 there was significant centralization similarities for 17 game lag. They went 48-34



```{r}
team_lag_graphs("NYK")
```

#New York Knicks
13-14 season 11 game lag show similarity in centralization. they went 37-45
14-15 season they also show 11 game lag similarity in centralization but went 17-65 and had a different coach
15-16 season has significant similarity in centralization for 1, 2, 3, and 5 game lags. they went 32-50 and had coaching change
16-17 only 3 game lag was close to being significant. went 31-51.
17-18 didn't have any significant centralization trends across all lags. Went 29-53



```{r}
team_lag_graphs("OKC")
```

#Oklahoma City
13-14 nothing significant. Went 59-23.
14-15 only positive values. 2, 4, and 6 game lag has similarites in centralization. 45-37, last year under scott brooks. Could have gotten too comfortable with Brooks and stopped changing game plan.
15-16 4 game lag had significance in centralization change, while 11 game lag had it in the positive. went 55-27 under first year with new coach Billy DOnovan.
16-17 significant 2 and 17 game lag for similarity in centralization. This is kind of similar to 14-15 season and with similar record of 47-35. After KD left and it was just Westbrook, Oladipo, and Steven Adams.
17-18 nothing sugnificant record was 48-34. Team had paul george, westbrook, adams, and carmelo.



```{r}
team_lag_graphs("ORL")
```

#Orlando
13-14 season had a 1 game lag sigificane for centralization similarity, they went 23-59
14-15 had a very significant 5 game lag for similarity but also a significant 13 game lag for differences in centralization. this team went 25-57
15-16 didn't have any significant values. They went 35-47
16-17 also didn't really have any significant values, and went 29-53.
17-18 didn't either and went 25-57. Was perennially bad but didn't show consistent trend in lags.



```{r}
team_lag_graphs("PHI")
```

#Philadelphia
13-14 had 12 game lag that was significant for differences in centralization. went 19-63
14-15 significant for 1 and 7 game lags for centralization similarity. Team went 18-64
15-16 only 10 game lag has significant similarity in centralization. Team went 10-72
16-17 no significant data team went 28-54.
17-18 no significant points, however, you see much more negative values across the lags and was the first time team had winning record 52-30



```{r}
team_lag_graphs("PHX")
```

#Phoenix
13-14 had no significant points, and went 48-34
14-15 had 1 and 3 game lag similarities for centralization. Team went 39-43.
15-16 had similar centralization for 2 and 5 game lags but different for 14 game lag and went 23-59
16-17 didn't have significant points and went 24-58
17-18 very strong 2 game lag for change in centralization went 21-61. Strongest value ive seen so far.



```{r}
team_lag_graphs("POR")
```

#Portland
13-14 no significant points. Went 54-28.
14-15 strong significance for 1 and 3 game lag as well as some for 17. went 51-31. What changed between season, team core was same Aldridge, lillard, mccollum, and same coach and similar record
15-16 no significant points and went 44-38. lost aldridge.
16-17 12 game lag is significant for centralization change. team went 41-41. Gained Nurkic
17-18 3 game lag has smililar centralization but 10 and 19 game lag have different centralizaiton trends. Team went 49-33. practically same team as year before



```{r}
team_lag_graphs("SAC")

```

#Sacramento




```{r}
team_lag_graphs("SAS")
```

#San Antonio
13-14 only significant point is the 5 game lag for change in centralization. went 62-29. This team won the finals. No one person averaged over 20 points a game. Parker, Duncan,  Leonard, Ginobili.
14-15 had high significance for 2 game lag. went 55-27. Same exact team as before with no one over 20ppg. lost western conference first round
15-16 high significance for 1, 2 and possibly 12 game lag. Went 67-15 for best record of the data set. Leonard had over 20ppg and aldridge joined team and Giniobili gone. lost western conference semis
16-17 no trends across lags. went 61-21. practically same team plus pau Gasol. lost conference finals
17-18 high significance for 15 and 16 game lag for similarity. had worst record of the five years at 47-35 still made playoffs lost first round. Leonard only played 9 games



```{r}
team_lag_graphs("TOR")
```

#Toronto
13-14 significance for 11 and 13 game lag in similarity of centralization. Team went 48-34
14-15 No significant data across lag went 49-33
15-16 no signigicant data across lag went 56-26
16-17 Significant for 3 and 6 game lag with centralization similarity. went 51-31.
17-18 only 13 game lag was significant and it was for difference in centralization. team went 59-23



```{r}
team_lag_graphs("UTA")
```

#UTAH
13-14 12 game lag for change in centralization but that is all. Team went 25-57
14-15 no significant points went 38-44
15-16 only significant point is 17 game lag for change in centralization team went 38-44
16-17 no significant points and team went 51-31
17-18 positive for 16 game lag where team went 48-34



```{r}
team_lag_graphs("WAS")
```

#Washington
13-14 no significant lag points teame went 44-38
14-15 no significant lag points team went 46-36
15-16 slight significance for 9 game lag in similarity of centralization, team went 41-41
16-17 no significant lag points team went 49-33
17-18 10, 14, and 19 game lag points for differences in centralizaion team went 43-39




