---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---


#In order to install this package you must have devtools installed. To do so type this into your console: install.packages("devtools")

#Once devtools is installed you will need to pull this package from github by typing this into your console: devtools::install_github("PatrickChodowski/NBAr")

#Once this is installed all you have to do is include NBAr in your library like I have done below by running: library(NBAr)

#These functions also require you to have the tidyverse library installed as well

**All the examples in the chuncks are meant to be examples for the parameters and may not run correctly or have an output**

#https://www.nba.com/players
#The above link will take you to the players page of the NBA website where you can find the Player ID numeber of any player you would be searching for. To do so jind the player you are looking for. Go to their individual page. The URL will contain the player ID number. For example LeBron James URL is: https://www.nba.com/player/2544/lebron-james so his player ID is 2544. 

#If you are looking for a game ID nunber use the get_schedule() function. The season that you put in the function is the season that it started in so if you are looking for a game in the 2018-2019 season you would do get_schedule(2018). The game IDs are on the left column.


#Libraries
```{r}
library(NBAr)
library(tidyverse)
```



#Example data 

#sample variables
```{r}
season <- 2018
gamelist <- c(21800001:21800003)
game_id <- 21800001
```
#Season variable represents the season we want to look at.
#amelist is a list of game id numbers according to the NBA website
#game id is a single game id number according to the NBA website




#get_boxscores()
## @param game_id Game's ID in NBA.com DB
## @param boxscore_type  Type of boxscore, one from the list: c("advanced","misc","playertrack","traditional")
## @param verbose Defalt TRUE - prints additional information
```{r}
traditional_multiple_games <- map(gamelist, ~get_boxscore(.,boxscore_type = 'traditional')) %>% compact() %>% bind_rows()

traditional <- get_boxscore(game_id, 'tradtitional')
```
##The traditional multiple games allows you to create a table of boxscores froma list of games. In the example it is a list of three games. The function get_boxscores wont let you do this by itself which is why the map is necessary. 
##The second is the use of the function on its own which takes in one game ID and returns the boxscore.
##Boxscore types include: advanced, misc, playertrack, and traditional.




#get_team_boxscore()
## @param season Number of the year in which season started
## @param measure_type Specify type of data   c('Base','Advanced','Four+Factors','Misc','Scoring')
## @param season_type Choose data for preseason, regular season or postseason. Default parameter is "Regular+Season". c("Regular+Season","Playoffs","Pre+Season","All+Star")
## @param game_segment Choose game half for the data. Empty string means whole game and it is set by default. c("","First+Half","Overtime","Second+Half")
# @param period Choose game period for the data. 0 means whole game and it is set by default. as.character(c(0:4))
## @param date_from Day from which data will be collected. It is set in MM/DD/YYYY format and by default is not specified, so data is calculated for whole season.
## @param date_to Day to which data will be collected. It is set in MM/DD/YYYY format and by default is not specified, so data is calculated for whole season.
## @param outcome Filter by game result. It can be a loss (L) or a win (W). By default parameter is an empty string, so both are taken into account. c("","W","L")
## @param opponent_team_id Filter by opponent's team id from nba.com database. Default "0" means all teams.
## @param verbose Defalt TRUE - prints additional information
```{r}
team_boxscores_all <- get_team_boxscore(season = 2018, date_from = '10/01/2018', date_to = '12/03/2018', measure_type = 'Advanced', outcome = 'W', season_type = "Regular+Season", opponent_team_id = "", period = "", game_segment = "")

team_boxscores <- get_team_boxscore(season)
```
##This only returns teams boxscores over the course of the season. That makes it a large table to sift through. You can use this in the most broad version shown by the second use which gives every boxscore for every team in one season. The first example allows you to filter certain parameters to find specific data. Note: you dont need to use all parameters, season is the only parameter you must imput.




#get_matchups 
## @param game_id Game's ID in NBA.com DB
## @param verbose Defalt TRUE - prints additional information
```{r}
matchup <- get_matchups(game_id)
```
##Gives in detail data on the player matchups that take place in one game. It gives you every matchup of offensive player vs defensive player and how many minutes it was and things such as shooting % against that defender. Could be really helpful for indepth analysis on single game player analysis or could be pulled together for larger player analysis vs a certain type of defender or person.




#get_playbyplay2
## @param game_id Game's ID in NBA.com DB
## @param verbose Defult TRUE - prints additional information
```{r}
pbp2 <- map(gamelist, ~get_playbyplay2(.)) %>% compact() %>% bind_rows()

pbp2_single_game <- get_playbyplay2(game_id)
```
##Gives you an extreamly detailed boxscore that has every action over the course of the game including where the ball was shot from, who was defending and more. The first example allows you to get a table that has the play by plays of more than one game. The game IDs must be in a list for the first example. The second example is the play by play of one game.




#get_lineups
## @param season Number of the year in which season started
## @param group_quantity Number of players in a lineup
## @param measure_type Type of statistics
## @param per_mode Specify if you want data divided per game or totals. Default parameter is "PerGame". c("PerGame","Totals")
## @param season_type Choose data for preseason, regular season or postseason. Default parameter is "Regular Season". c("Regular Season","Playoffs","Pre Season","All Star")
## @param season_segment Choose season half for the data. Empty string means whole season and it is set by default. c("","Post All-Star","Pre All-Star")
## @param game_segment Choose game half for the data. Empty string means whole game and it is set by default. c("","First Half","Overtime","Second Half")
## @param date_from Day from which data will be collected. It is set in MM/DD/YYYY format and by default is not specified, so data is calculated for whole season.
## @param date_to Day to which data will be collected. It is set in MM/DD/YYYY format and by default is not specified, so data is calculated for whole season.
## @param outcome Filter by game result. It can be a loss (L) or a win (W). By default parameter is an empty string, so both are taken into account. c("","W","L")
## @param opponent_team_id Filter by opponent's team id from nba.com database. Default "0" means all teams.
## @param team_id Specify team id from nba.com database. Default "0" means all teams.
## @param verbose Defalt TRUE - prints additional information
```{r}
#' example1 <- get_lineups(season = '2017',
#'               group_quantity = 5,
#'               measure_type = "Base",
#'               team_id="0",
#'               date_from="",
#'               date_to="",
#'               opponent_team_id="0",
#'               outcome="",
#'               per_mode="Totals",
#'               season_segment="",
#'               game_segment="",
#'               season_type="Regular+Season")


lineups <- get_lineups(season, 5, 'Base')
bulls_lineups <- get_lineups(season, 5, 'Base', team_id = 1610612741)
```
##Gives you the player ids and names of the lineups of certain players across teams. Allows you to look at different variables across certain lineups like W/L as well as other statistics. The second example is pulling a specific teams lineups as opposed to the whole leagues. The top section that is parsed out is the full ability of the function and all the parameters you can use. The exaples shown do not use all of the parameters. 




#get_on_off
#3 @param season Number of the year in which season started
## @param per_mode Specify if you want data divided per game or totals. Default parameter is "PerGame". c("PerGame","Totals")
## @param period Choose game period for the data. 0 means whole game and it is set by default. as.character(c(0:4))
## @param season_type Choose data for preseason, regular season or postseason. Default parameter is "Regular Season". c("Regular Season","Playoffs","Pre Season","All Star")
## @param season_segment Choose season half for the data. Empty string means whole season and it is set by default. c("","Post All-Star","Pre All-Star")
## @param game_segment Choose game half for the data. Empty string means whole game and it is set by default. c("","First Half","Overtime","Second Half")
## @param date_from Day from which data will be collected. It is set in MM/DD/YYYY format and by default is not specified, so data is calculated for whole season.
## @param date_to Day to which data will be collected. It is set in MM/DD/YYYY format and by default is not specified, so data is calculated for whole season.
## @param outcome Filter by game result. It can be a loss (L) or a win (W). By default parameter is an empty string, so both are taken into account. c("","W","L")
## @param opponent_team_id Filter by opponent's team id from nba.com database. Default "0" means all teams.
## @param team_id Specify team id from nba.com database. Default "0" means all teams.
## @param verbose Defalt TRUE - prints additional information
```{r}
#' example =     get_on_off(season = 2017,
#'                 team_id = 1610612739,
#'                 measure_type,
#'                 date_from="",
#'                 date_to="",
#'                 opponent_team_id="0",
#'                 outcome="",
#'                 period = as.character(1),
#'                 per_mode=per_mode,
#'                 season_segment="",
#'                 game_segment="",
#'                 season_type="Regular+Season")


onoff_bulls <- get_on_off(season, 1610612741)
```
##Gives a list of the players of a team for a given season. The table contains statistics for every players time while on and off the court such as plus/minus and offensive and defensive ratings. It also lists how many games they played in and total minutes played that season. The first one that is parsed out is the full capability of this function and all of its parameters. The only parameters you have to have is the season and the team ID.




#get_players & get_playerbio
## @param season Number of the year in which season started
## @param only_current 0 To show historical list of all players 1 to show only current season
## @param verbose Defalt TRUE - prints additional information
```{r}
#' example <-   get_players(season = 2018, only_current = 1)


players <- get_players(season)
player_bio <- get_playerbio(season)
```
##Get players gives you a list of players that played that season. there is a parameter that allows you to look at players who played only in the season you are looking at as opposed to a historical list. Player bio gives you physical attribues of players that year as well as their stats from the season you input.




#get_shotchart
## @param player_id Player's ID in NBA.com DB
## @param season Number of the year in which season started
## @param context_measure Specify which value group you want to download. c('PTS','FGA','FGM','FG_PCT','FG3M','FG3A','FG3_PCT','PF',
## 'EFG_PCT','TS_PCT','PTS_FB','PTS_OFF_TOV','PTS_2ND_CHANCE')
## @param per_mode Specify if you want data divided per game or totals. Default parameter is "PerGame". c("PerGame","Totals")
## @param season_type Choose data for preseason, regular season or postseason. Default parameter is "Regular Season". c("Regular Season","Playoffs","Pre Season","All Star")
## @param season_segment Choose season half for the data. Empty string means whole season and it is set by default. c("","Post All-Star","Pre All-Star")
## @param game_segment Choose game half for the data. Empty string means whole game and it is set by default. c("","First Half","Overtime","Second Half")
## @param period Choose game period for the data. 0 means whole game and it is set by default. as.character(c(0:4))
## @param date_from Day from which data will be collected. It is set in MM/DD/YYYY format and by default is not specified, so data is calculated for whole season.
## @param date_to Day to which data will be collected. It is set in MM/DD/YYYY format and by default is not specified, so data is calculated for whole season.
## @param outcome Filter by game result. It can be a loss (L) or a win (W). By default parameter is an empty string, so both are taken into account. c("","W","L")
## @param opponent_team_id Filter by opponent's team id from nba.com database. Default "0" means all teams.
## @param verbose Defalt TRUE - prints additional information
```{r}
#`example <- get_shotchart(player_id = 203518, 
#`                         season = 2018,
#`                         context_measure = "FG_PCT",
#`                         date_from = "01/01/2017",
#`                         date_to = "04/30/2017",
#`                         game_segment = "First+Half",
#`                         period = "0",
#`                         per_mode = "PerGame",
#`                         outcome = "W",
#`                         season_type = "Regular+Season",
#`                         season_segment = "Post+All+Star",
#`                         opponent_team_id = "0",
#`                         verbose = TRUE)


shots_abrines <- get_shotchart(203518, season)
```
##Has very discriptive data on every shot for every player over the course of a season. In order to make sense of this data it would be useful to manipulate it or possibly put it into a chart. Doesnt produce a graph or chart instead a table. There are a lot of parameters that you can use to filter through to get very specific shooting data. The only parameters you need to have are player ID and season.




#get_schedule
## @param season Number of the year in which season started
## @param verbose Defult TRUE - prints additional information
```{r}
schedule <- get_schedule(season)
```
Gives you the complete NBA schedule for the selected season.




#get_tracking
## @param season Number of the year in which season started
## @param type Specify if data is for Team or Player   c("Player,"Team")
## @param measure_type Specify which statistics group you want to download. c("Drives","Defense","CatchShoot","Passing","Possessions","PullUpShot","Rebounding","Efficiency","SpeedDistance","ElbowTouch","PostTouch","PaintTouch")[1]
## @param per_mode Specify if you want data divided per game or totals. Default parameter is "PerGame". c("PerGame","Totals")
## @param season_type Choose data for preseason, regular season or postseason. Default parameter is "Regular+Season". c("Regular+Season","Playoffs","Pre+Season","All+Star")
## @param season_segment Choose season half for the data. Empty string means whole season and it is set by default. c("","Post+All-Star","Pre+All-Star")
## @param game_segment Choose game half for the data. Empty string means whole game and it is set by default. c("","First+Half","Overtime","Second+Half")
## @param period Choose game period for the data. 0 means whole game and it is set by default. as.character(c(0:4))
## @param date_from Day from which data will be collected. It is set in MM/DD/YYYY format and by default is not specified, so data is calculated for whole season.
## @param date_to Day to which data will be collected. It is set in MM/DD/YYYY format and by default is not specified, so data is calculated for whole season.
## @param outcome Filter by game result. It can be a loss (L) or a win (W). By default parameter is an empty string, so both are taken into account. c("","W","L")
## @param opponent_team_id Filter by opponent's team id from nba.com database. Default "0" means all teams.
## @param verbose Defalt TRUE - prints additional information
```{r}
#' example <- get_tracking(
#'                                 season = 2018,
#'                                 type = "Team",
#'                                 measure_type = "Passing",
#'                                 per_mode = "Totals",
#'                                 season_type = "Regular+Season",
#'                                 season_segment = "Post+All+Star",
#'                                 game_segment = "First+Half",
#'                                 date_from = "01/01/2019",
#'                                 date_to = "04/01/2019",
#'                                 outcome = "W",
#'                                 period = as.character(1),
#'                                 opponent_team_id = "0"
#'                                 )


tracking <- get_tracking(season, 'Team',measure_type = 'Defense')
```
##You can track different measures by teams or player by season. You can change your measure type to track different things. You must have a season, type, and measure type, all other parameters are optional. This doesn't allow you to pull up all measure types at once, that is what get_all_tracking does




#get_all_tracking
#' @param season Number of the year in which season started
#' @param type Specify if data is for Team or Player   c("Player,"Team")
#' @param measure_types Specify which statistics group you want to download. c("Drives","Defense","CatchShoot","Passing","Possessions","PullUpShot","Rebounding","Efficiency","SpeedDistance","ElbowTouch","PostTouch","PaintTouch")
#' @param ... Additional arguments for get_tracking
```{r}
all_tracking <- get_all_tracking(season, "Team")
```
##This is similar to tracking, the difference here is you dont need to put a measure types in and it will return all of them where the one above needs that variable described. You can also put in more than one type and measure type and look through players and teams and certain measure types if you dont want all of them.




#get_playtype
## @param season Number of the year in which season started
## @param type Specify if data is for Team or Player   c("P,"T")
## @param per_mode Specify PerGame or Totals c("PerGame","Totals")
## @param playtype Pick one of the playtypes provided by stats.nba.com. c("Postup","Transition","Isolation","PRBallHandler","PRRollman","Spotup","Handoff","Cut","OffScreen","OffRebound","Misc")
## @param type_grouping Specify if data is for offensive or defensive side of the floor. c("offensive","defensive")
## Warning! 'Transition','Cut','OffRebound', 'Misc' do not work for defensive!
## @param season_type Choose data for preseason, regular season or postseason ("Regular+Season","Playoffs")
## @param verbose Defalt TRUE - prints additional information
```{r}
#'example <- get_playtype(season = 2018,
#'                        type = "T",
#'                        playtype = "Postup",
#'                        type_grouping = "offensive",
#'                        season_type = "Regular+Season",
#'                        per_mode = "Totals",
#'                        verbose = TRUE)


playtype <- get_playtype(season, 'T', 'Postup')
```
##Allows you to look at all 32 teams, or by players, and how they perform givern a certain playtype. The team aspect of this would be more useful to us. As stated above in the parameters, you cant use playtype transition, cut, offrebound, or misc when you type grouping is defense.




#get_genteral
## @param season Number of the year in which season started
## @param type Specify if data is for Team or Player   c("Player,"Team")
## @param measure_type Specify which statistics group you want to download. c("Base","Advanced","Misc","Scoring","Usage","Opponent","Defense", "Four+Factors")
## @param per_mode Specify if you want data divided per game or totals. Default parameter is "PerGame". c("PerGame","Totals")
## @param season_type Choose data for preseason, regular season or postseason. Default parameter is "Regular+Season". c("Regular+Season","Playoffs","Pre+Season","All+Star")
## @param season_segment Choose season half for the data. Empty string means whole season and it is set by default. c("","Post+All-Star","Pre+All-Star")
## @param game_segment Choose game half for the data. Empty string means whole game and it is set by default. c("","First+Half","Overtime","Second Half")
## @param period Choose game period for the data. 0 means whole game and it is set by default. as.character(c(0:4))
## @param date_from Day from which data will be collected. It is set in MM/DD/YYYY format and by default is not specified, so data is calculated for whole season.
## @param date_to Day to which data will be collected. It is set in MM/DD/YYYY format and by default is not specified, so data is calculated for whole season.
## @param outcome Filter by game result. It can be a loss (L) or a win (W). By default parameter is an empty string, so both are taken into account. c("","W","L")
## @param opponent_team_id Filter by opponent's team id from nba.com database. Default "0" means all teams.
## @param team_id Specify team id from nba.com database. Default "0" means all teams.
## @param verbose Defalt TRUE - prints additional information
```{r}
#' example <- get_general(
#'                             season = "2018",
#'                             type = "Team",
#'                             measure_type = "Advanced",
#'                             per_mode = "Totals",
#'                             season_type = "Regular+Season",
#'                             season_segment = "Post+All+Star",
#'                             game_segment = "First+Half",
#'                             date_from = "01/01/2018",
#'                             date_to = "03/30/2018",
#'                             outcome = "W",
#'                             period = as.character(1),
#'                             opponent_team_id = "0",
#'                             team_id = "0"
#'                             )

general <- get_general(season, type = 'Team', 'Base')
```
##Oragnized by teams or by players. This has general team info and organizes them across multiple statistics and ranks them in these statistics out of the 32 teams, or the amount of players in the search, rather than the numeric value of the statistic

#get_hustle
#' @param game_id Game's ID in NBA.com DB
#' @param verbose Defalt TRUE - prints additional information
```{r}
hustle <- get_hustle(game_id)
```
##This might be the most interesting as it is the "hustle" stats that dont show up on a normal stat sheet. This gives you these stats per game. It includes things such as deflections, charges drawn, loose balls recovered, boxouts, etc. This is broken down by player within the game. The number in the function is a game ID




#get_shooting
## @param season Number of the year in which season started
## @param type Specify if data is for Team or Player   c("Player,"Team")
## @param distance_range Specify how do you want to split the basketball court c("5ft Range","8ft Range","By Zone")
## @param measure_type Specify if you want data for offensive (base) or defensive(opponent) shooting per player or per team. c("Base","Opponent")
## @param per_mode Specify if you want data divided per game or totals. Default parameter is "PerGame". c("PerGame","Totals")
## @param season_type Choose data for preseason, regular season or postseason. Default parameter is "Regular Season". c("Regular Season","Playoffs","Pre Season","All Star")
## @param season_segment Choose season half for the data. Empty string means whole season and it is set by default. c("","Post All-Star","Pre All-Star")
## @param game_segment Choose game half for the data. Empty string means whole game and it is set by default. c("","First Half","Overtime","Second Half")
## @param period Choose game period for the data. 0 means whole game and it is set by default. as.character(c(0:4))
## @param date_from Day from which data will be collected. It is set in MM/DD/YYYY format and by default is not specified, so data is calculated for whole season.
## @param date_to Day to which data will be collected. It is set in MM/DD/YYYY format and by default is not specified, so data is calculated for whole season.
## @param outcome Filter by game result. It can be a loss (L) or a win (W). By default parameter is an empty string, so both are taken into account. c("","W","L")
## @param opponent_team_id Filter by opponent's team id from nba.com database. Default "0" means all teams.
## @param team_id Specify team id from nba.com database. Default "0" means all teams.
## @param verbose Defalt TRUE - prints additional information
```{r}
#' example <- get_shooting(
#'                                 season = "2018",
#'                                 type = "Team",
#'                                 distance_range = "By Zone",
#'                                 measure_type = "Base",
#'                                 per_mode = "Totals",
#'                                 season_type = "Regular+Season",
#'                                 season_segment = "Post+All+Star",
#'                                 game_segment = "",
#'                                 date_from = "01/01/2018",
#'                                 date_to = "03/30/2018",
#'                                 outcome = "W",
#'                                 period = as.character(1),
#'                                 opponent_team_id = 0,
#'                                 team_id = 0
#'                                 )

shooting <- get_shooting(season, 'Team', "By+Zone", "Base")
```
##Breaks down shooting by team. Each teams shooting is broken down by sections of the court such as restricted area, paint, midrange, and different areas of the 3-point land. It contains shooting percentage from every area as well. Can be broken down by player as well. The only parameters that must be filled are season, type, distance range, and measure type.




#get_shooting_dashboard
#' @param season Number of the year in which season started
#' @param type Specify if data is for Team or Player   c("Player,"Team")
#' @param general_range = c("Overall","Catch+And+Shoot","Pullups","Less+Than+10+ft")
#' @param shot_clock_range = c("24-22","22-18+Very+Early","18-15+Early","15-7+Average","7-4+Late","4-0+Very+Late","ShotClock+Off")
#' @param dribble_range = c("0+Dribbles","1+Dribble","2+Dribbles","3-6+Dribbles","7++Dribbles")
#' @param touch_time_range = c("Touch+<+2+Seconds","Touch+2-6+Seconds","Touch+6++Seconds")
#' @param close_def_dist_range = c("0-2+Feet+-+Very+Tight","2-4+Feet+-+Tight","4-6+Feet+-+Open","6++Feet+-+Wide+Open")
#' @param shot_dist_range = c("","> 3D10.0")
#' @param per_mode Specify if you want data divided per game or totals. Default parameter is "PerGame". c("PerGame","Totals")
#' @param season_type Choose data for preseason, regular season or postseason. Default parameter is "Regular+Season". c("Regular+Season","Playoffs","Pre+Season","All+Star")
#' @param season_segment Choose season half for the data. Empty string means whole season and it is set by default. c("","Post+All-Star","Pre+All-Star")
#' @param game_segment Choose game half for the data. Empty string means whole game and it is set by default. c("","First+Half","Overtime","Second+Half")
#' @param period Choose game period for the data. 0 means whole game and it is set by default. as.character(c(0:4))
#' @param date_from Day from which data will be collected. It is set in MM/DD/YYYY format and by default is not specified, so data is calculated for whole season.
#' @param date_to Day to which data will be collected. It is set in MM/DD/YYYY format and by default is not specified, so data is calculated for whole season.
#' @param outcome Filter by game result. It can be a loss (L) or a win (W). By default parameter is an empty string, so both are taken into account. c("","W","L")
#' @param opponent_team_id Filter by opponent's team id from nba.com database. Default "0" means all teams.
#' @param team_id Specifyteam id from nba.com database. Default "0" means all teams.
#' @param verbose Defalt TRUE - prints additional information
```{r}
#' example <- get_shooting_dashboard(
#'                           season = 2018,
#'                           type = "Team",
#'                           general_range = "Overall",
#'                           shot_clock_range = "22-18+Very+Early",
#'                           dribble_range = "0+Dribbles",
#'                           touch_time_range "Touch+<+2+Seconds",
#'                           close_def_dist_range "0-2+Feet+-+Very+Tight",
#'                           shot_dist_range = "",
#'                           per_mode = "Totals",
#'                           season_type = "Regular+Season",
#'                           season_segment = "Post+All+Star",
#'                           game_segment = "",
#'                           date_from = "01/01/2018",
#'                           date_to = "03/30/2018",
#'                           outcome = "W",
#'                           period = as.character(2),
#'                           opponent_team_id = 0,
#'                           team_id = 0
#'                           )


shooting_dashboard <- get_shooting_dashboard(season = 2018, type = "Team")
```
##This is a further breakdown of the shooting function. It allows you to look deeper into things such as shotclock range, dribble range, shot distance range, and touch time range. The only parameters you need to have are season and type




#get_defense
## @param season Number of the year in which season started
## @param type Specify if data is for Team or Player   c("Player","Team")
## @param defense_category Specify which defense category data you need. c("Overall","3+Pointers","2+Pointers","Less+Than+6Ft","Less+Than+10Ft","Greater+Than+15Ft")
## @param per_mode Specify if you want data divided per game or totals. Default parameter is "PerGame". c("PerGame","Totals")
## @param season_type Choose data for preseason, regular season or postseason. Default parameter is "Regular Season". c("Regular Season","Playoffs","Pre Season","All Star")
## @param season_segment Choose season half for the data. Empty string means whole season and it is set by default. c("","Post All-Star","Pre All-Star")
## @param game_segment Choose game half for the data. Empty string means whole game and it is set by default. c("","First Half","Overtime","Second Half")
## @param period Choose game period for the data. 0 means whole game and it is set by default. as.character(c(0:4))
## @param date_from Day from which data will be collected. It is set in MM/DD/YYYY format and by default is not specified, so data is calculated for whole season.
## @param date_to Day to which data will be collected. It is set in MM/DD/YYYY format and by default is not specified, so data is calculated for whole season.
## @param outcome Filter by game result. It can be a loss (L) or a win (W). By default parameter is an empty string, so both are taken into account. c("","W","L")
## @param opponent_team_id Filter by opponent's team id from nba.com database. Default "0" means all teams.
## @param team_id Specify team id from nba.com database. Default "0" means all teams.
## @param verbose Defalt TRUE - prints additional information
```{r}
#' example <- get_defense(
#'                           season = 20118,
#'                           type = 'Team',
#'                           defense_category = 'Overall',
#'                           per_mode = 'Totals',
#'                           season_type = "Regular+Season",
#'                           season_segment = "Post+All+Star",
#'                           game_segment = "",
#'                           date_from = "01/01/2018",
#'                           date_to = "03/30/2018",
#'                           outcome = "W",
#'                           period = as.character(1),
#'                           opponent_team_id = 0,
#'                           team_id = 0
#'                           )

defense <- get_defense(season = 2018, type = 'Team', defense_category = 'Overall', per_mode = 'Totals')
```
##Is sorted by the 32 teams in this example but can aslo be sorted by players. Can look through deffensive ratings and stats based on what kind of shot they are defending, i.e. the defense_category. The only parameters that you must fill are season, type, and defense category.




#get_news
#' @param limit Default 100, choose how many recent news you want
#' @param verbose Defalt TRUE - prints additional information
```{r}
news <- get_news(limit = 10)
```
##Doesnt seem to work for whatever reason. It is supposed to return a data set with weekly news. Doesnt seem too important to what we are doing. limit is the number of recent news you want, defult is 100.




#get_player_movement
## @param verbose Defult TRUE - prints additional information
```{r}
player_movement <- get_player_movement()
```
This function gets all the roster tansactions since 2015. Is similar to the data that we had last semester where we were looking at player transactions. This data set might be even more indepth than the one we worked with




#get_rotowire_status
## @param verbose Defalt TRUE - prints additional information
```{r}
rotowire_status <- get_rotowire_status()
```
I get a similar error to that of the funciton to get news. 



