---
title: "Relative Standing"
output: html_notebook
---

## Libraries 
```{r}
library(tidyverse)
library(data.table)
library(lubridate)
library(readxl)
```
## Data 
```{r}
Player_data <- fread("~/Downloads/nba_pass_data_14_18_individual.csv")
```
## Relative standing Across the Entire League (Made)
```{r}

Player_data %>% filter(PASS_TYPE == "made") %>% group_by(slugSeason, idGame, PLAYER_ID) %>% summarise(passes = sum(PASS)) %>% mutate(Relative = scale(passes))

```
## Relative standing Across the Entire League (Received)
```{r}

Player_data %>% filter(PASS_TYPE == "received") %>% group_by(slugSeason, idGame, PLAYER_ID) %>% summarise(passes = sum(PASS)) %>% mutate(Relative = scale(passes)) %>% filter(PLAYER_ID == "1882")

```
## Relative standing within the team (Mdde)
```{r}

Player_data %>% filter(PASS_TYPE == "made") %>% group_by(TEAM_NAME, idGame, PLAYER_ID) %>% summarise(passes = sum(PASS)) %>% mutate(Relative = scale(passes)) 

```
## Relative standing within the team (Received)
```{r}

Player_data %>% filter(PASS_TYPE == "received") %>% group_by(TEAM_NAME, idGame, PLAYER_ID) %>% summarise(passes = sum(PASS)) %>% mutate(Relative = scale(passes)) %>% filter(PLAYER_ID == "1882")

```
## Relative standing within the team, by season (Made)
```{r}

Player_data %>% filter(PASS_TYPE == "made") %>% group_by(slugSeason, TEAM_NAME, idGame, PLAYER_ID) %>% summarise(passes = sum(PASS)) %>% mutate(Relative = scale(passes))

```
## Relative standing within the team, by season (Received)
```{r}

Player_data %>% filter(PASS_TYPE == "received") %>% group_by(slugSeason, TEAM_NAME, idGame, PLAYER_ID) %>% summarise(passes = sum(PASS)) %>% mutate(Relative = scale(passes))

```
## Percetage of passes for each player in each game 
```{r}

Player_data %>% group_by(slugSeason, idGame, PLAYER_ID, TEAM_NAME, TEAM_ABBREVIATION, PASS_TYPE) %>% nest() 

```
## Test Area
```{r}

summarise(passes = sum(PASS)) %>% mutate(Relative = scale(passes)) 
  ggplot(aes(x = passes)) + geom_density()
  
  Player_data %>% filter(PASS_TYPE == "made") %>% count(PASS, idGame, PLAYER_ID) 
  
  mutate(percentage = n/sum(n))
  
```

